---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# sims

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.com/lifecycle/#experimental)
[![Travis-CI Build Status](https://travis-ci.com/poissonconsulting/sims.svg?branch=master)](https://travis-ci.com/poissonconsulting/sims)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/poissonconsulting/sims?branch=master&svg=true)](https://ci.appveyor.com/project/poissonconsulting/sims)
[![Coverage Status](https://img.shields.io/codecov/c/github/poissonconsulting/sims/master.svg)](https://codecov.io/github/poissonconsulting/sims?branch=master)
<!-- badges: end -->

sims is an R package to simulate and manipulate datasets.

## Installation

To install the latest development version from [GitHub](https://github.com/poissonconsulting/sims)
```
remotes::install_github("poissonconsulting/sims")
```

To install the latest development version from the Poisson drat [repository](https://github.com/poissonconsulting/drat)
```
drat::addRepo("poissonconsulting")
install.packages("sims")
```

## Demonstration

### Simulate Data

The `sims_generate()` function allows the user to simulate data 
using JAGS model code.

By default, it returns the simulated datasets in the form of a nlists object.

```{r example}
library(sims)
set.seed(10)
sims_generate("a ~ dunif(0,1)", nsims = 2L)
```

If `write = TRUE` then the datasets are saved as `.rds` files.
The key sims_generate function arguments are saved in `argsims.rds`.
```{r}
set.seed(10)
sims_generate("a ~ dunif(0,1)", nsims = 2L,
                       write = TRUE, path = tempdir(), exists = NA)
```
Additional datasets can be generated using `sims_add()`
```{r}
sims_add(path = tempdir(), nsims = 3L)
```

And the argsims and data files copied to a new directory using `sims_copy()`
```{r}
sims_copy(path_from = tempdir(), path_to = paste0(tempdir(), "_copy"))
```

The internal consistency of a set of generated data can be queried using `sims_check()`.
```{r}
sims_check(path = paste0(tempdir(), "_copy"))
```

```{r example2}
library(sims)
set.seed(10L)

likelihood <- "
 # Likelihood: Note key components of a GLM on one line each
 rand ~ dnorm(0,1)
 for (i in 1:n){
   C[i] ~ dpois(lambda[i])          # 1. Distribution for random part
   log(lambda[i]) <- log.lambda[i]  # 2. Link function
   log.lambda[i] <- alpha + beta1 * year[i] + beta2 * pow(year[i],2) + beta3 * pow(year[i],3)                      # 3. Linear predictor
   } #i
 "
 monitor=c("C", "rand")

 values <- list(alpha = 3.5576,
                beta1 = -0.0912,
                beta2 = 0.0091,
                beta3 = -0.00014,
                n = 5,
                year = 1:5)
 
 nsims=5
 
 results <- sims_generate(code=likelihood, constants=values, monitor=monitor, nsims=nsims)
 
 results
 
 results[,"C"]
 results[,"rand"]
 
 #Now I want to present those in the following format so I can pass them as data to JAGS for the analysis
 # nlist objects should be able to be feed in element by element to JAGs models.
 
  str(results)
```

