---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# sims

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.com/lifecycle/#experimental)
[![Travis-CI Build Status](https://travis-ci.com/poissonconsulting/sims.svg?branch=master)](https://travis-ci.com/poissonconsulting/sims)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/poissonconsulting/sims?branch=master&svg=true)](https://ci.appveyor.com/project/poissonconsulting/sims)
[![Coverage Status](https://img.shields.io/codecov/c/github/poissonconsulting/sims/master.svg)](https://codecov.io/github/poissonconsulting/sims?branch=master)
<!-- badges: end -->

sims is an R package to simulate, save and manipulate datasets.
The generative model is specified using a fragment of JAGS code.

## Installation

To install the latest development version from [GitHub](https://github.com/poissonconsulting/sims)
```
remotes::install_github("poissonconsulting/sims")
```

To install the latest development version from the Poisson drat [repository](https://github.com/poissonconsulting/drat)
```
drat::addRepo("poissonconsulting")
install.packages("sims")
```

## Demonstration


```{r example2}
library(sims)
set.seed(10L)

generative_model <- "
rand ~ dnorm(0,1)
for (i in 1:length(Year)){
  C[i] ~ dpois(lambda[i])
  log(lambda[i]) <- alpha + beta1 * Year[i]
}
"

parameters <- list(alpha = 3.5576, beta1 = -0.0912)

constants <- list(Year = 1:5)

results <- sims_generate(generative_model, 
                         constants = constants,
                         parameters = parameters)

results

results[[1]]
```

### Simulate Data

By default, `sims_generate()` returns the simulated datasets in the form of an nlists object.

```{r example}
library(sims)
set.seed(10)
sims_generate("a ~ dunif(0,1)", nsims = 2L)
```

If, however, `write = TRUE` then each nlist object is saved as an `.rds` files.
The information used to generate the datasets is saved in `argsims.rds`.
```{r}
set.seed(10)
sims_generate("a ~ dunif(0,1)", nsims = 2L,
              write = TRUE, path = tempdir(), exists = NA)
```
The fact that the arguments to sims_generate() are saved in `argsims.rds` allows additional datasets to be generated using `sims_add()`.
```{r}
sims_add(path = tempdir(), nsims = 3L)
```

If the user wishes to duplicate the datasets then can either regenerate them by specifying a different path but the same key.
Alternatively, they can copy the existing argsims and datasets files to a new directory using `sims_copy()`
```{r}
sims_copy(path_from = tempdir(), path_to = paste0(tempdir(), "_copy"))
```

A user can check that all the datasets specified in `argsims.rds` are present using `sims_check()`.
```{r}
sims_check(path = paste0(tempdir(), "_copy"))

file.remove(file.path(paste0(tempdir(), "_copy"), "data0000005.rds"))
```

```{r, error = TRUE}
sims_check(path = paste0(tempdir(), "_copy"))
```

# Contribution

Please report any [issues](https://github.com/poissonconsulting/sims/issues).

[Pull requests](https://github.com/poissonconsulting/sims/pulls) are always welcome.

Please note that the 'sims' project is released with a [Contributor Code of Conduct](https://poissonconsulting.github.io/sims/CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
