---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# sims

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.com/lifecycle/#experimental)
[![Travis-CI Build Status](https://travis-ci.com/poissonconsulting/sims.svg?branch=master)](https://travis-ci.com/poissonconsulting/sims)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/poissonconsulting/sims?branch=master&svg=true)](https://ci.appveyor.com/project/poissonconsulting/sims)
[![Coverage Status](https://img.shields.io/codecov/c/github/poissonconsulting/sims/master.svg)](https://codecov.io/github/poissonconsulting/sims?branch=master)
<!-- badges: end -->

sims is an R package to simulate and analyse data using JAGS.

## Installation

To install the latest development version from [GitHub](https://github.com/poissonconsulting/sims)
```
remotes::install_github("poissonconsulting/sims")
```

To install the latest development version from the Poisson drat [repository](https://github.com/poissonconsulting/drat)
```
drat::addRepo("poissonconsulting")
install.packages("sims")
```


## Demonstration

### Simulate Data

The `sims_nlist()` function allows the user to simulate data 
using JAGS model code.

It returns the simulated data values in the form of a single chain `mcmcr::mcmcr` 
object where each iteration represents one sample.

```{r example}
library(sims)
set.seed(10L)
sims_nlist("a ~ dunif(0,1)", nsims = 1L)
```


```{r example2}
library(sims)
set.seed(10L)

likelihood <- "
 # Likelihood: Note key components of a GLM on one line each
 rand ~ dnorm(0,1)
 for (i in 1:n){
   C[i] ~ dpois(lambda[i])          # 1. Distribution for random part
   log(lambda[i]) <- log.lambda[i]  # 2. Link function
   log.lambda[i] <- alpha + beta1 * year[i] + beta2 * pow(year[i],2) + beta3 * pow(year[i],3)                      # 3. Linear predictor
   } #i
 "
 monitor=c("C", "rand")

 values <- list(alpha = 3.5576,
                beta1 = -0.0912,
                beta2 = 0.0091,
                beta3 = -0.00014,
                n = 5,
                year = 1:5)
 
 nsims=5
 
 results <- sims_nlist(code=likelihood, constants=values, monitor=monitor, nsims=nsims)
 results$C[1,,]
 results$rand[1,,]
 
 #Now I want to present those in the following format so I can pass them as data to JAGS for the analysis

listres<-vector("list", nsims)
within <- vector("list", length(names(results)))
names(within) <- names(results)
listres <- lapply(listres, function(x)within)
listres

#But I can only get them in the following unlisted format:

 f<- function(x) results[[x[1]]][1,x[2],]
 unlisted <- apply(expand.grid(1:length(monitor),1:nsims), 1, f)
 unlisted
 
 #How can I match those?
```

