---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# bayesims

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis-CI Build Status](https://travis-ci.org/poissonconsulting/bayesims.svg?branch=master)](https://travis-ci.org/poissonconsulting/bayesims)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/poissonconsulting/bayesims?branch=master&svg=true)](https://ci.appveyor.com/project/poissonconsulting/bayesims)
[![Coverage Status](https://img.shields.io/codecov/c/github/poissonconsulting/bayesims/master.svg)](https://codecov.io/github/poissonconsulting/bayesims?branch=master)<!-- badges: end -->

bayesims is an R package to simulate data using JAGS code.

## Installation

To install the development version from the Poisson drat [repository](https://github.com/poissonconsulting/drat)
``` r
install.packages("bayesims", repos = "http://poissonconsulting.github.io/drat")
```

## Demonstration

### Simulate Data

The `bsm_simulate_data()` function allows the user to simulate data 
using JAGS model code.

It returns the simulated data values in the form of a single chain `bayesims::bayesims` 
object where each iteration represents one sample.

```{r example}
library(bayesims)
set.seed(10L)
bsm_simulate_data("a ~ dunif(0,1)", nsamples = 1L)
```
