---
title: "Using sims"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using sims}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(sims)
```

```{r example}
library(sims)
set.seed(10)
sims_simulate("a ~ dunif(0,1)", nsims = 2L)
```

If, however, `save = TRUE` then each nlist object is saved as an `.rds` file in `path`.
```{r}
set.seed(10)
sims_simulate("a ~ dunif(0,1)", nsims = 2L, save = TRUE, path = tempdir(), exists = NA)
sims_data_files(tempdir())
sims_data(tempdir())
```


The information used to generate the datasets is saved in `.sims_args.rds`.
The fact that the arguments to `sims_simulate()` are saved to file allows additional `.rds` datasets to be generated using `sims_add()`.
```{r}
sims_add(tempdir(), nsims = 3L)
sims_data_files(tempdir())
```

If the user wishes to duplicate the datasets then they can either regenerate them by specifying a different path but the same seed.
Alternatively, they can copy the existing `.sims.rds` and datasets files to a new directory using `sims_copy()`
```{r}
sims_copy(path_from = tempdir(), path_to = paste0(tempdir(), "_copy"))
```

A user can check that all the datasets specified in `.sims.rds` are present using `sims_check()`.
```{r}
sims_check(path = paste0(tempdir(), "_copy"))
```

```{r, error = TRUE}
file.remove(file.path(paste0(tempdir(), "_copy"), "data0000005.rds"))

sims_check(path = paste0(tempdir(), "_copy"))
```

## Parallelization

Parallelization is achieved using the [future](https://github.com/HenrikBengtsson/future) package.

To use all available cores on the local machine simply execute the following code before calling `sims_simulate()`.
```{r}
library(future)
plan(multisession)
```

```{r}
set.seed(10)
sims_simulate("a ~ dunif(0,1)", nsims = 2L)
```
